### 2024-04-22 parts/appendix.tex
typos
moving remark to appendix

\begin{proof}[Proof of \cref{negative-but-npoly:ex}]
    Remark that $P = (X-1)^2 + 1$. Let $f  \colon \Sigma^* \to \Nat$
    that maps $aw \mapsto |w|^2$, and $\varepsilon \to 0$.
    It is clear that $f \in \NPoly$, and that 
    $P$ is \kl{represented} by
    $\ind{|w| \geq 1} \times f + \ind{|w| = 0}$.
\end{proof}

@@

>>>>

\begin{proofof}[negative-but-npoly:ex]
    Remark that $P = (X-1)^2 + 1$. Let $f  \colon \Sigma^* \to \Nat$
    that maps $aw \mapsto |w|^2$, and $\varepsilon \to 0$.
    It is clear that $f \in \NPoly$, and that 
    $P$ is \kl{represented} by
    $\ind{|w| \geq 1} \times f + \ind{|w| = 0}$.
\end{proofof}

@@

As one would expect, the \kl{discrete derivatives} are linear operations on
polynomials, that commutes with \kl{translation operators}. However, the
\kl{translation operators} do not perfectly commute with partial applications
$\restr{\cdot}{\nu}$.

\begin{remark}
    \label{discrete-deriv-linear:fact}
    For all tuples $\vec{X}$ of indeterminates,
    for all $K \in \Nat$, $L \in \Rel$, for all partial functions
    $\nu \colon \vec{X} \topartial \Nat$:
    \begin{enumerate}
        \item The maps $\translate{K} \colon \Rel[\vec{X}] \to \Rel[\vec{X}]$,
        $\Diff{K}{ \cdot } \colon \Rel[\vec{X}] \to \Rel[\vec{X}]$,
        and
        $\restr{\cdot}{\nu} \colon \Rel[\vec{X}] \to \Rel[\vec{X}]$
            are linear operators,
        \item $\Diff{K}{ \cdot } \circ \translate{L}
            = \translate{L} \circ \Diff{K}{\cdot}$,
        \item $\restr{\cdot}{\nu} \circ \translate{L}
            = \translate{L} \circ \restr{\cdot}{\translate{L}(\nu)}$.
    \end{enumerate}
\end{remark}
